---
title: "Mycale grandis Substrate Association Analysis"
author: "Emily C Rutkowski"
format: html
---

```{r setup, include = FALSE} 
# include = FALSE means this code runs but doesnt show in output 
# set up global options for the whole quarto document 
knitr::opts_chunk$set(echo = TRUE, # show code in output 
                      warning = FALSE, # dont show warnings
                      message = FALSE, # dont show messsages 
                      fig.width = 10, # set default fig width 
                      fig.height = 6) # set default fig height 

```

# Introduction 

This analysis examines whether **Mycale grandis (MG)** shows a preferential association with **Porites compressa** live coral beyond what would be expected based on substrate availability alone.

**Research Question:** Does Mycale grandis attach to Porites compressa simply because it's abundant, or does it show a true preference for this substrate?

```{r load-packages}
# Load libraries
library(tidyverse) # tidyverse for everything
library(readxl) # to read excel files
library(patchwork) # to combine plots
library(scales) # for better plot formatting 
library(VGAM) # for beta-binomial regression 
library(here)
```

# Load in Data 

```{r load-data}
# Read the Mycale grandis (MG) substrate association data
# This file contains the percentage of MG on each substrate type per transect 
mg_substrate<- read_csv(here("..", "data", "permgsubassoc.csv"))

```

